### 2014-11-13 tex/evaluation.tex
Proofreading, fixing typos.
polishing of evaluation section

The results of the experiments are presented in Table
\ref{tab:results}. The rows contain to individual $k$-bounded test
runs for each of the evaluated programs. The columns show the total
walk clock time in seconds, states explored, and paths generated for
each of the algorithms. The headings \gsetxt{}, L\#, and SL correspond
to the Generalized Symblic Execution, lazier\#, and \symtxt{}
algorithms, respectively. Note that we do no present the results for
lazier algorithm since they are almost identical to that of lazier\#
for our examples. Table entries containing - correspond to test runs
that exceeded the allotted time bounds. Each trial is time bounded to
10 mins.

>>>>

The results of the experiments are presented in Table
\ref{tab:results}. Each row contains the results for the specified $k$-bound 
for each artifact evaluated. The columns show the total
wall clock time in seconds, states explored, and paths generated for
each of the algorithms. The headings \gsetxt{}, L\#, and SL correspond
to the Generalized Symblic Execution, lazier\#, and \symtxt{}
algorithms, respectively. Note that we do no present the results for
lazier algorithm since they are almost identical to that of lazier\#
for our examples. Table entries containing - correspond to test runs
that exceeded the allotted time bounds. Each trial is time bounded to
10 mins.
